Homework 2

### 2016-10-09 Statistical Learning/Homework2/assignment.tex
update

\problem{1}{Explain the relationship between spectral clustering, normalized spectral clustering and graph cut.}
\solution{Solution}{
We assume $k=2$ in the following explanation. \n
For spectral clustering, we already know that the eigenvector $u_2$ corresponding to the second smallest eigenvalue $\lambda_2$ of the Laplacian matrix of the graph is the solution for the minimization
$$ \min_{\tbf{f}} \ \tbf{f}^\top\tbf{L}\tbf{f},$$
$$s.t. \quad \tbf{f}^\top \tbf{f} = 1, \tbf{f}^\top\tbf{1} = 0$$
In fact, if we define 
$$G(f) = G(f_1, \cdots)$$
For Min Cut, if we define $\tbf{f} = (f_1, f_2\cdots f_n)\tr$
}

>>>>

\problem{1}{Explain the relationship between spectral clustering, normalized spectral clustering and graph cut.}
\solution{Solution}{
We assume $k=2$ in the following explanation. \n
For spectral clustering, we already know that the eigenvector $u_2$ corresponding to the second smallest eigenvalue $\lambda_2$ of the Laplacian matrix of the graph is the solution for the minimization
$$ \min_{\tbf{f}} \ \tbf{f}^\top\tbf{L}\tbf{f},$$
$$s.t. \quad \tbf{f}^\top \tbf{f} = 1, \tbf{f}^\top\tbf{1} = 0$$
In fact, if we define 
$$G(f) = G(f_1,\cdots, f_n) = f\tr\tbf{L}f - \lambda_1 (f\tr f-1) - \lambda_2 f\tr\tbf{1} $$ $$ =  \frac{1}{2}\sum_{i,j=1}^{n}w_{ij}(f_i-f_j)^2-\lambda_1(\sum_{i=1}^{n}f_i^2-1)-\lambda_2\sum_{i=1}^n f_i$$
Then according to Lagrange Theorm, we let
$$\frac{\partial G}{\partial f_i} = \sum_{j=1}^n (f_i-f_j) - 2\lambda_1 f_i - \lambda_2 = 0, \quad  i=1:n$$
If we add the $n$ equations, we get
$$2\lambda_1\sum_{i, j=1}^n f_i + n\lambda_2=0$$
Since $f\tr\tbf{1} = 0$, then $\lambda_2 = 0$. So
$$\sum_{j=1}^n w_{ij}f_{j} = \lambda f_i, \quad i=1:n,$$
which means $f$ is an eigenvector of $\tbf{L}$.\n
For Min Cut, if we define $\tbf{f} = (f_1, f_2\cdots f_n)^\top$
}
